### 2016-10-16 Kokkos_PG_HierarchicalParallelism.tex
Updates Hierarchical Parallelism

This chapter explains how to use Kokkos to exploit multiple levels of shared-memory parallelism.
These levels include thread teams, threads within a team, and vector lanes.
You may nest these levels of parallelism,
and execute \lstinline!parallel_for!, \lstinline!parallel_reduce!, or \lstinline!parallel_scan! at each level.
The syntax differs only by the execution policy,
which is the first argument to the \verb!parallel_*! operation.
Kokkos also exposes a ``scratch pad'' memory which all threads within a team may share.

@@

@@

Kokkos exposes use of thread teams with the \lstinline!Kokkos::TeamPolicy! execution policy.
To use thread teams you need to create a \lstinline|Kokkos::TeamPolicy| instance.
It can be created inline for the parallel dispatch call.
The constructors requires two arguments: a league size and a team size. 
In place of the team size a user can utilize \lstinline|Kokkos::AUTO| to let Kokkos guess a good team size for a given architecture.
Doing that is the recommend way for most developers to utilize the \lstinline|TeamPolicy|.
As with the  \lstinline|Kokkos::RangePolicy| a specific execution tag and a specific execution space can be given as optional template arguments.
\begin{lstlisting}
// Using default execution space and launching 
// a league with league_size teams with team_size threads each
Kokkos::TeamPolicy<> 
        policy( league_size, team_size );

@@

\subsection{Basic kernels}\label{SS:Hierarchical:Teams:Kernels}

>>>>

This chapter explains how to use Kokkos to exploit multiple levels of shared-memory parallelism.
These levels include thread teams, threads within a team, and vector lanes.
You may nest these levels of parallelism,
and execute \lstinline!parallel_for!, \lstinline!parallel_reduce!, or \lstinline!parallel_scan! at each level.
The syntax differs only by the execution policy,
which is the first argument to the \verb!parallel_*! operation.
Kokkos also exposes a ``scratch pad'' memory which provides thread private and team private allocations..

@@

You should use Hierarchical Parallelism in particular in a number of cases:
\begin{enumerate}
\item Non-tightly nested loops: Hierarchical Parallelism allows you to expose more parallelism.
\item Data gather + reuse: If you gather data for a particular iteration of an outer loop, and then repeatiptly use it in an inner loop, Hierarchical Parallelism with scratch memory may match the usecase well.
\item Force Cache Blocking: Using Hierarchical Parallelism forces a developer into algorithmic choices which are good for cache blocking. This can sometimes lead to better performing algorithms, than simple flat parallelism.
\end{enumarate}

On the other hand you should probably not use Hierarchical Parallelism if you have tightly nested loops. 
For that usecase a multi dimensional RangePolicy is the better fit.

@@

Kokkos exposes use of thread teams with the \lstinline!Kokkos::TeamPolicy! execution policy.
To use thread teams you need to create a \lstinline|Kokkos::TeamPolicy| instance.
It can be created inline for the parallel dispatch call.
The constructors requires two arguments: a league size and a team size. 
In place of the team size a user can utilize \lstinline|Kokkos::AUTO| to let Kokkos guess a good team size for a given architecture.
Doing that is the recommend way for most developers to utilize the \lstinline|TeamPolicy|.
As with the  \lstinline|Kokkos::RangePolicy| a specific execution tag, a specific execution space, a \lstinline|Kokkos::IndexType|, and a \lstinline|Kokkos::Schedule| can be given as optional template arguments.
\begin{lstlisting}
// Using default execution space and launching 
// a league with league_size teams with team_size threads each
Kokkos::TeamPolicy<> 
        policy( league_size, team_size );

@@

\subsection{Basic kernels}\label{SS:Hierarchical:Teams:Kernels}:
